---
title: "Final Assignment - CSC8631"
author: "Chatwipa Surapat"
date: "2024-11-13"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r, include=FALSE}
library(ProjectTemplate)
load.project()
library(dplyr)
library(knitr)
library(ggplot2)
library(scales)
library(tidyverse)
library(gridExtra)
library(grid)
```

# First investigation
## Business Understanding
Online learning is one of the learning method that popular nowadays due to their accessibility and flexibility. However, most of students un-enroll the course after a few day or some of them un-enroll right after start the first section which is the primary problem of the online learning. Therefore, one of the challenge for online lesson provider is how to reduce the number of un-enrollment student.

### 1.1 Business objectives and success criteria
The objective of this report is to analyse the factors contributing to student withdrawal in order to gain insights to understand the issues and identify strategies for improving the course. The analysis will cover the reasons for student withdrawal, the progression of course improvements over time, and potential enhancements for future course.

### 1.2 Requirement, assumption, and constrains
The data set in this analysis come from the “Cyber Security: Safety At Home, Online, and in Life” course made by `Newcastle University` which public and collect the data through `FutureLearn`, virtual learning provider. The un-enrollment survey which include the information about reason of un-enrollment, withdrawal dates and learning hours are the primary information that used for the analysis.

The R project template is used to structure and organize the analysis to ensure that the analysis results can be reproduced. Additionally, this project also backs up and records versions using Git to track changes during the development period.

The students withdrawal survey is expected to identify the issues of course and address the course improvement method. However, some survey responses may be incomplete, as some question in the survey is compulsory. Consequently, the analysis results may not represent the entire student population.

### 1.3 Risk and contingencies
As student survey is the primary source that used for analysis, which relies on user-provided input. Consequently, it might contain missing response in some question that might effect to the analysis result. Therefore, the data set will be cleaned and selected the relevant responses for analysis, depending on the specific business question being addressed.

## Data Understanding
### 2.1 Initial data collection
There are seven different runs of the online course, resulting in seven distinct sets of survey responses. The types of survey responses vary across each run. In the first run, there were only five summary files including archetype, enrollment, leaving survey, quiz response, activity log and sentiment survey. In the second run, a team member survey was introduced. After that, video-watching statistics were also recorded and included in the data set. 

### 2.2 Data exploration
Overall, the number of enrolled students decreased over time, with a low number of students fully participating. The percentage of unenrolled students relative to enrolled students was approximately 10% in the first five runs, but it shows a significant decrease in the sixth and seventh runs, suggesting that there may have been some changes to the course in the last two runs.

```{r, echo = FALSE}
enrollment_summary <- enroll_survey_all |>
  group_by(run_number) |>
  summarize(total = n(),
            complete = sum(!is.na(fully_participated_at)),
            complete_percentage = (complete / total) * 100,
            unenroll = sum(!is.na(unenrolled_at)),
            unenroll_percentage = (unenroll / total) * 100)

kable(enrollment_summary, 
      caption = "Enrollment summary", 
      digits = 2, align = "c",
      col.names = c("Run No.", "Enrollments", 
                    "Full Participation", "% Full Participation", 
                    "Un-enrollments", "% Un-enrollment"))
```
However, some of the response files are empty. The details of empty files of each runs are provided in the table below, where "x" indicates an empty file and "o" indicates a present file.

```{r, echo=FALSE}
table_data <- data.frame(
  `No Run` = 1:7,
  Archetype = c("x", "x", "o", "o", "o", "o", "o"),
  Enrollment = c("o", "o", "o", "o", "o", "o", "o"),
  Leave = c("x", "x", "x", "o", "o", "o", "o"),
  Quiz = c("o", "o", "o", "o", "o", "o", "o"),
  Activity = c("o", "o", "o", "o", "o", "o", "o"),
  Team = c("x", "o", "o", "o", "o", "o", "o"),
  Video = c("x", "x", "o", "o", "o", "o", "o"),
  Sentiment = c("x", "x", "x", "x", "o", "o", "o")
)

# Print the table with a caption
kable(table_data, align = "c", caption = "Summary of different survey files")
```
From this summary table, quantitative data on un-enrollment can be observed across different runs. However, it is important to note that there are no leaving survey response in the first three runs, which limits insights into student withdrawal reasons for those runs.

Two survey responses, including *cyber.security.n_leaving.survey.responses* and *cyber.security.n_enrolments*, are used as the primary files for the un-enrollment analysis, where "n" represents the run number. The leaving survey contains 403 observations with 9 variables across all runs, while the enrollment survey contains 37,296 observations with 14 variables. The *learner_id* variable is present in both files and can be used to join these two files together. Additionally, there is one variable about time stamp of un-enrollment that present in both data frame but use the different name. For better understanding, the description of each column that used in this analysis are summarized in the table below.

```{r, echo=FALSE}
table_data <- data.frame(
  Column = c("learner_id", "enrolled_at", "unenrolled_at", "left_at", "age_range", 
             "employment_status", "leaving_reason"),
  Description = c("Unique identifier for each student", 
                  "Time stamp of enrollment", 
                  "Time stamp of un-enrollment (same as `left_at`)", 
                  "Time stamp of un-enrollment (same as `unenrolled_at`)", 
                  "Age range of the student", 
                  "Current employment status of the student", 
                  "Reason of leaving the course"),
  Survey = c("Leave, Enrollment", "Enrollment", "Enrollment", "Leave", 
             "Enrollment", "Enrollment", "Leave")
)

# Print the table with kable
kable(table_data, align = c("l", "l", "c"), 
      caption = "Description of used survey columns")
```

## Data preparation
The pre-processing script is stored in the `munge` folder of the project template. This file will be processed automatically upon starting the project for the first time. The pre-processed file will then be stored in the `cache` folder to reduce processing time for subsequent runs. In this investigation, `01-Combined_leave` serves as the primary file for pre-processing the data. Only *cyber.security.n_leaving.survey.responses* and *cyber.security.n_enrolments* are selected to analyze factors related to learner un-enrollment.

Firstly, all columns related to time in both response files were processed to convert the data type to `POSIX` time. Then, rows from each type of survey response were combined to generate two data frames including all leaving surveys and enrollment surveys, with the adding of running number column for separation. Finally, both data frames were joined by `full_join()` function that matching the *learner_id* column to create the `preprocessed_leave` data frame for analysis. This method will keep all observations in both data frame and add the `NA` value in the empty field.

The pre-processed data frame contains 37,304 observations across 21 variables, which is higher than the total rows in *cyber.security.n_enrolments*. This increase is due to some learners providing multiple responses to questions, resulting in multiple entries for the same learner ID in the leaving survey.

```{r, include = FALSE}
duplicate_leave <- leave_survey_all |>
  group_by(learner_id, run_number) |>
  filter(n() > 1)

cat("Number of Duplicate IDs (Leave survey):", nrow(duplicate_leave), "\n")

duplicate_enroll <- enroll_survey_all |>
  group_by(learner_id, run_number) |>
  filter(n() > 1)

cat("Number of Duplicate IDs (Enroll survey):", nrow(duplicate_enroll), "\n")
```

## Modeling

```{r, echo=FALSE, fig.width=12, fig.height=4, fig.cap="Percentage of enrollment status"}
enrollment_summary <- enroll_survey_all |>
  group_by(run_number) |>
  summarize(uncomplete = n(),
            complete = sum(!is.na(fully_participated_at)),
            unenroll = sum(!is.na(unenrolled_at))) |>
  pivot_longer(cols = c(uncomplete, complete, unenroll), 
               names_to = "status", 
               values_to = "count") |>
  group_by(run_number) |>
  mutate(total = sum(count),
         percentage = count / total * 100)


# Stacked bar plot
stack_plot <- ggplot(enrollment_summary,
                     aes(x = fct_rev(factor(run_number, levels = sort(unique(run_number), decreasing = TRUE))),
                         y = count, fill = status)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(count >= 500, count, "")),
            position = position_stack(vjust = 0.5), color = "white", size = 3) +
  labs(x = "Count", y = "Run Number", fill = "Enrollment Status") +
  theme_minimal() +
  scale_fill_manual(values = c("uncomplete" = "gray", "complete" = "#fc8d62", "unenroll" = "#66c2a5"))

# 100% stacked bar plot
stack_100_plot <- ggplot(enrollment_summary,
                         aes(x = fct_rev(factor(run_number, levels = sort(unique(run_number), decreasing = TRUE))),
                             y = percentage, fill = status)) +
  geom_bar(stat = "identity", position = "fill") +
  geom_text(aes(label = ifelse(percentage >= 4, paste0(round(percentage, 0), "%"), "")), 
            position = position_fill(vjust = 0.5), color = "white", size = 3) +
  labs(x = "Percentage", y = "Run Number", fill = "Enrollment Status") +
  theme_minimal() +
  scale_fill_manual(values = c("uncomplete" = "gray", "complete" = "#fc8d62", "unenroll" = "#66c2a5"))


grid.arrange(stack_plot, stack_100_plot, ncol = 2, nrow = 1)

```
The stacked bar chart illustrates the distribution of enrollment status across all course runs. The number of enrollments significantly drop at the second run and continues to decrease gradually in subsequent runs. The 100% stack bar chart supports that there may have been a significant change in the course structure during the second run, leading to a higher percentage of student withdrawals and lower number of enrollment. Additionally, they may have been some change in the third run causing slightly decrease of withdrawal number.

Upon reviewing the course overview, the second run of this course introduced additional steps to the course structure: 1 step in the first section and 2 steps in the second section. However, the third run removed one step from the final session. These change may have influenced the student withdrawal rate.

```{r, echo=FALSE, fig.width=12, fig.height=3.5, fig.cap="Distribution of leaving reasons"}
leave_reason_counts <- leave_survey_all |>
  group_by(run_number) |>
  count(leaving_reason)

# Define a custom color palette based on integer run numbers
custom_colors <- c("4" = "#e66101", 
                   "5" = "#fdb863",  
                   "6" = "#b2abd2",
                   "7" = "#5e3c99") 

# Ensure your run_number is treated as a factor for plotting
leave_reason_counts$run_number <- as.factor(leave_reason_counts$run_number)

ggplot(leave_reason_counts, aes(x = leaving_reason, y = n, fill = run_number)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(n > 5, n, "")), 
            position = position_stack(vjust = 0.5), color = "white", size = 4) +
  theme_minimal() +
  labs(x = "Reasons",
       y = "Count",
       fill = "No. Run") + 
  scale_x_discrete(labels = label_wrap(20)) +
  scale_fill_manual(values = custom_colors)
```
The chart shows that time management is the primary problem making learner withdraw the course, observing from high counts of I don’t have enough time" and "The course required more time than I realized" categories. There are low number of student that withdraw the course due to skill alignment, course difficulty and course expectations, indicating the the difficulty level of this course might be generally acceptable for most of students. In addition, there are high number of students that withdraw the course from other reasons.

These data suggest that the number of steps in the course is an important factor influencing the withdrawal rate. Many students encounter time management problems, increasing the number of steps in the course may contribute to higher withdrawal rates. However, since the course structure has remained unchanged after the third run and the percentage of student withdrawal consistently decrease, suggesting that the structure of this course may now be suitable for the average learner. Therefore, skill alignment and managing student expectations are two areas that could be improved in future runs.

This report proposes two potential solutions to enhance course performance. First, introducing a pre-test exam before enrollment could help students understand the overall content provided in this course. If a student scores high on the pre-test, it may suggest that the course is too easy for them. In contrast, if a student cannot answer all the questions provided, it may suggest that the course is too challenging for them at this time, and they may need to study some background knowledge before enrolling. Second, providing a expected learning outcomes to student before enrollment is one of the possible solutions. The summary of learning outcome would help student access whether the course aligns with their expectations.

## Evaluation


# Second investigation





