---
title: "Final Assignment - CSC8631"
author: "Chatwipa Surapat"
date: "2024-11-13"
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r, include=FALSE}
library(ProjectTemplate)
load.project()
```

# 1. First investigation
## 1.1 Business Understanding
Online learning is one of the learning method that popular nowadays due to their accessibility and flexibility. However, most of students un-enroll the course after a few day or some of them un-enroll right after start the first section which is the primary problem of the online learning. Therefore, one of the challenge for online lesson provider is how to reduce the number of un-enrollment student.

### 1.1.1 Business objectives and success criteria
The objective of this report is to analyse the factors contributing to student withdrawal in order to gain insights to understand the issues and identify strategies for improving the course. The analysis should cover the reasons for student withdrawal, the progression of course improvements over time, and potential enhancements for future course.

### 1.1.2 Requirements, assumptions, and constrains
The data set in this analysis come from the “Cyber Security: Safety At Home, Online, and in Life” course made by `Newcastle University` which public and collect the data through `FutureLearn`, virtual learning provider. The un-enrollment survey which include the information about reason of un-enrollment, withdrawal dates and learning hours are the primary information that used for the analysis.

The R project template is used to structure and organize the analysis to ensure that the analysis results can be reproduced. Additionally, this project also backs up and records versions using Git to track changes during the development period.

The students withdrawal survey is expected to identify the issues of course and address the course improvement method. However, some survey responses may be incomplete, as some question in the survey is compulsory. Consequently, the analysis results may not represent the entire student population.

### 1.1.3 Risk and contingencies
As student survey is the primary source that used for analysis, which relies on user-provided input. Consequently, it might contain missing response in some question that might effect to the analysis result. Therefore, the data set will be cleaned and selected the relevant responses for analysis, depending on the specific business question being addressed.

## 1.2 Data Understanding
### 1.2.1 Initial data collection
There are seven different runs of the online course, resulting in seven distinct sets of survey responses. The types of survey responses vary across each run. In the first run, there were only five summary files including archetype, enrollment, leaving survey, quiz response, activity log and sentiment survey. In the second run, a team member survey was introduced. After that, video-watching statistics were also recorded and included in the data set. 

### 1.2.2 Data exploration
The course structure was provided in `.pdf` format. There are three sections in this course, including exploring personal privacy online, online payment security, and future home security. However, there have been some changes to the course structure across runs, which might be one of the factors affecting un-enrollment.

Overall, the number of enrolled students decreased over time, with a low number of students fully participating. The percentage of unenrolled students relative to enrolled students was approximately 10% in the first five runs, but it shows a significant decrease in the sixth and seventh runs, suggesting that there may have been some changes to the course in the last two runs.

```{r, echo = FALSE}
enrollment_summary <- enroll_survey_all |>
  group_by(run_number) |>
  summarize(total = n(),
            complete = sum(!is.na(fully_participated_at)),
            complete_percentage = (complete / total) * 100,
            unenroll = sum(!is.na(unenrolled_at)),
            unenroll_percentage = (unenroll / total) * 100)

kable(enrollment_summary, 
      caption = "Enrollment summary", 
      digits = 2, align = "c",
      col.names = c("Run No.", "Enrollments", 
                    "Full Participate", "%Full Participate", 
                    "Un-enrollment", "%Un-enrollment"))
```
However, some of the response files are empty. The details of empty files of each runs are provided in the table below, where "x" indicates an empty file and "o" indicates a present file.

```{r, echo=FALSE}
table_data <- data.frame(
  `No Run` = 1:7,
  Archetype = c("x", "x", "o", "o", "o", "o", "o"),
  Enrollment = c("o", "o", "o", "o", "o", "o", "o"),
  Leave = c("x", "x", "x", "o", "o", "o", "o"),
  Quiz = c("o", "o", "o", "o", "o", "o", "o"),
  Activity = c("o", "o", "o", "o", "o", "o", "o"),
  Team = c("x", "o", "o", "o", "o", "o", "o"),
  Video = c("x", "x", "o", "o", "o", "o", "o"),
  Sentiment = c("x", "x", "x", "x", "o", "o", "o")
)

# Print the table with a caption
kable(table_data, align = "c", caption = "Summary of different survey files")
```
From this summary table, quantitative data on un-enrollment can be observed across different runs. However, it is important to note that there are no leaving survey response in the first three runs, which limits insights into student withdrawal reasons for those runs.

Two survey responses, including *cyber.security.n_leaving.survey.responses* and *cyber.security.n_enrolments*, are used as the primary files for the un-enrollment analysis, where "n" represents the run number. The *learner_id* variable is present in both files and can be used to join these two files together. Additionally, there is one variable about time stamp of un-enrollment that present in both data frame but use the different name. For better understanding, the description of each column that used in this analysis are summarized in the table below.

```{r, echo=FALSE}
table_data <- data.frame(
  Column = c("learner_id", "enrolled_at", "unenrolled_at", "left_at",
             "employment_status", "leaving_reason"),
  Description = c("Unique identifier for each student", 
                  "Time stamp of enrollment", 
                  "Time stamp of un-enrollment (same as `left_at`)", 
                  "Time stamp of un-enrollment (same as `unenrolled_at`)",
                  "Current employment status of the student", 
                  "Reason of leaving the course"),
  Survey = c("Leave, Enrollment", "Enrollment", "Enrollment", "Leave", 
             "Enrollment", "Leave")
)

# Print the table with kable
kable(table_data, align = c("l", "l", "c"), 
      caption = "Description of used survey columns")
```

## 1.3 Data preparation
The pre-processing script is stored in the `munge` folder of the project template. This file will be processed automatically upon starting the project for the first time. The pre-processed file will then be stored in the `cache` folder to reduce processing time for subsequent runs. In this investigation, `01-Combined_leave` serves as the primary file for pre-processing the data. Only *cyber.security.n_leaving.survey.responses* and *cyber.security.n_enrolments* are selected to analyze factors related to learner un-enrollment.

Firstly, all columns related to time in both response files were processed to convert the data type to `POSIX` time and change curly apostrophe to the standard apostrophe. Then, rows from each type of survey response were combined to generate two data frames including all leaving surveys and enrollment surveys, with the adding of running number column for separation. The leaving survey contains 403 observations with 9 variables across all runs, while the enrollment survey contains 37,296 observations with 14 variables. Finally, both data frames were joined by `full_join()` function that matching the *learner_id* column to create the `preprocessed_leave` data frame for analysis. This method will keep all observations in both data frame and add the `NA` value in the empty field.

The pre-processed data frame contains 37,304 observations across 21 variables, which is higher than the total rows in *cyber.security.n_enrolments*. This increase is due to some learners providing multiple responses to questions, resulting in multiple entries for the same learner ID in the leaving survey.

```{r, include = FALSE}
duplicate_leave <- leave_survey_all |>
  group_by(learner_id, run_number) |>
  filter(n() > 1)

cat("Number of Duplicate IDs (Leave survey):", nrow(duplicate_leave), "\n")

duplicate_enroll <- enroll_survey_all |>
  group_by(learner_id, run_number) |>
  filter(n() > 1)

cat("Number of Duplicate IDs (Enroll survey):", nrow(duplicate_enroll), "\n")
```

### 1.4 Modeling

```{r, echo=FALSE, fig.cap="Percentage of enrollment status", fig.width=12, fig.height=4}
enrollment_summary <- enroll_survey_all |>
  group_by(run_number) |>
  summarize(uncomplete = n(),
            complete = sum(!is.na(fully_participated_at)),
            unenroll = sum(!is.na(unenrolled_at))) |>
  pivot_longer(cols = c(uncomplete, complete, unenroll), 
               names_to = "status", 
               values_to = "count") |>
  group_by(run_number) |>
  mutate(total = sum(count),
         percentage = count / total * 100)


# Stacked bar plot
stack_plot <- ggplot(enrollment_summary,
                     aes(x = fct_rev(factor(run_number, levels = sort(unique(run_number), decreasing = TRUE))),
                         y = count, fill = status)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(count >= 500, count, "")),
            position = position_stack(vjust = 0.5), color = "white", size = 3) +
  labs(x = "Count", y = "Run Number", fill = "Enrollment Status") +
  theme_minimal() +
  scale_fill_manual(values = c("uncomplete" = "gray", "complete" = "#fc8d62", "unenroll" = "#66c2a5"))

# 100% stacked bar plot
stack_100_plot <- ggplot(enrollment_summary,
                         aes(x = fct_rev(factor(run_number, levels = sort(unique(run_number), decreasing = TRUE))),
                             y = percentage, fill = status)) +
  geom_bar(stat = "identity", position = "fill") +
  geom_text(aes(label = ifelse(percentage >= 4, paste0(round(percentage, 0), "%"), "")), 
            position = position_fill(vjust = 0.5), color = "white", size = 3) +
  labs(x = "Percentage", y = "Run Number", fill = "Enrollment Status") +
  theme_minimal() +
  scale_fill_manual(values = c("uncomplete" = "gray", "complete" = "#fc8d62", "unenroll" = "#66c2a5"))

grid.arrange(stack_plot, stack_100_plot, ncol = 2, nrow = 1)
```


The stacked bar chart illustrates the distribution of enrollment status across all course runs. The number of enrollments significantly drop at the second run and continues to decrease gradually in subsequent runs. The 100% stack bar chart supports that there may have been a significant change in the course structure during the second run, leading to a higher percentage of student withdrawals and lower number of enrollment. Additionally, they may have been some change in the third run causing slightly decrease of withdrawal number.

Upon reviewing the course overview, the second run of this course introduced additional steps to the course structure: 1 step in the first section and 2 steps in the second section. However, the third run removed one step from the final session. These change may have influenced the student withdrawal rate.

```{r, echo=FALSE, fig.cap="Distribution of leaving reasons", fig.width=12, fig.height=4}
leave_reason_counts <- leave_survey_all |>
  group_by(run_number) |>
  count(leaving_reason)

# Define a custom color palette based on integer run numbers
custom_colors <- c("4" = "#e66101", 
                   "5" = "#fdb863",  
                   "6" = "#b2abd2",
                   "7" = "#5e3c99") 

# Ensure your run_number is treated as a factor for plotting
leave_reason_counts$run_number <- as.factor(leave_reason_counts$run_number)

ggplot(leave_reason_counts, aes(x = leaving_reason, y = n, fill = run_number)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(n > 5, n, "")), 
            position = position_stack(vjust = 0.5), color = "white", size = 4) +
  theme_minimal() +
  labs(x = "Reasons",
       y = "Count",
       fill = "No. Run") + 
  scale_x_discrete(labels = label_wrap(20)) +
  scale_fill_manual(values = custom_colors)
```


The chart shows that time management is the primary problem making learner withdraw the course, observing from high counts of I don’t have enough time" and "The course required more time than I realized" categories. There are low number of student that withdraw the course due to skill alignment, course difficulty and course expectations, indicating the the difficulty level of this course might be generally acceptable for most of students. In addition, there are high number of students that withdraw the course from other reasons.

These data suggest that the number of steps in the course is an important factor influencing the withdrawal rate. Many students encounter time management problems, increasing the number of steps in the course may contribute to higher withdrawal rates. However, since the course structure has remained unchanged after the third run and the percentage of student withdrawal consistently decrease, suggesting that the structure of this course may now be suitable for the average learner. 

This report proposes three potential solutions to enhance course performance. First, providing a study plan may help students see the time required for this course and the timeline for completion more clearly. For example, students could be given an estimate of study hours per week, and the platform could then generate a personalized study plan based on this information. This would enhance students’ ability to manage their time and reduce withdrawal rate. Second, introducing a pre-test exam before enrollment could help students understand the overall content provided in this course. If a student scores high on the pre-test, it may suggest that the course is too easy for them. In contrast, if a student cannot answer all the questions provided, it may suggest that the course is too challenging for them at this time, and they may need to study some background knowledge before enrolling. Lastly, providing a expected learning outcomes to student before enrollment is one of the possible solutions. The summary of learning outcome would help student access whether the course aligns with their expectations. 

## 1.5 Evaluation
In this investigation, the analysis shows that time management is the most common reason for un-enrollment. However, skill alignment and course expectations are also challenges that should be addressed to improve future course performance. The data shows that the withdrawal rate consistently decreases after the course structure adjustment in the third run, indicating that the current course structure is suitable for most learners. Additionally, three possible solutions have been suggested based on the data findings to enhance course performance. Therefore, this report achieve the success criteria because it can answer all questions in the section 1.1.1.

However, the most important factor of un-enrollment rate that could not identify in this investigation is the quality of the course. Thus, the survey responses from fully participate learner should be used to evaluate the course quality in the next investigation round.

# 2. Second investigation
## 2.1 Business Understanding
The quality of the course is one of the key factors that needs to be evaluated. The data show that although the percentage of student un-enrollment has decreased over time, the number of enrollments has also declined. Therefore, this investigation aims to analyse student satisfaction.

### 2.1.1 Business objectives and success criteria
The objective of this report is to analyse student satisfaction for this course. The analysis will cover overall experience ratings and satisfaction trends. Additionally, sentiment analysis will identify areas for improvement by examining both positive and negative opinions.

### 2.1.2 Requirements, assumptions, and constrains
All requirements and constraints from the first investigation (section 1.1.2) continue to apply. This investigation assumes that the experience ratings provided by students, along with sentiment analysis, can effectively address the overall satisfaction with the course.

### 2.1.3 Risk and contingencies
The sentiment response was collected only from the last two runs, the findings may not fully represent student sentiments across all runs. Moreover, the accuracy of sentiment analysis depends on the quality of data. Furthermore, the accuracy of sentiment analysis depends on data quality. Therefore, if this analysis reveals that data quality is insufficient, further data collection may be necessary.

## 2.2 Data Understanding
### 2.2.1 Initial data collection
There are seven sentiment survey responses file that provided in this data set. However, only the files in sixth and seventh runs that contain the student responses. 

### 2.2.2 Data exploration
*cyber.security.n_weekly.sentiment.survey.responses* is the primary file for this analysis, where "n" represents the run number. For better understanding, the description of each column that used in this analysis are summarized in the table below.

```{r, echo=FALSE}
table_data <- data.frame(
  Column = c("id", "responded_at", "week_number", "experience_rating", "reason"),
  Description = c("Unique identifier for each student", 
                  "The timestamp when the survey response was submitted.",
                  "Week of the course during which the survey was taken",
                  "A numeric rating given by the student",
                  "Feedback provided by the student"))

kable(table_data, align = c("l", "l"), 
      caption = "Description of column in sentiment survey")
```
Although this data set has 7 runs, there are only fifth, sixth and seventh run that have the sentiment responses. The detail of sentiment survey responses are provided in the table below.

```{r, echo = FALSE}
enrollment_summary <- enroll_survey_all |>
  group_by(run_number) |>
  summarize(total = n(),
            complete = sum(!is.na(fully_participated_at))
            ,)

sentiment_summary <- preprocessed_sentiment |>
  group_by(run_number) |>
  summarize(response = n_distinct(id), .groups = "drop")

sentiment_enrollment_summary <- full_join(enrollment_summary, sentiment_summary,
                                by = c( "run_number")) |>
  mutate(response = replace_na(response, 0))

kable(sentiment_enrollment_summary, 
      caption = "Sentiment survey summary", 
      digits = 2, align = "c",
      col.names = c("Run No.", "Total Enrollment",
                    "Full Participate", 
                    "Total Responses"))
```
In the fifth run, there is only one response from 22 learners who fully participated in the course. However, the table shows that the number of survey responses in the sixth and seventh runs is greater than the number of learners who completed the course, indicating that this survey includes not only students who completed the course but also those who were currently studying.

### 2.3 Data preparation
In this investigation, `02-Combined_sentiment` serves as the primary file for pre-processing the data. Only *cyber.security.n_weekly.sentiment.survey.responses* is selected to analyze learner satisfaction. This pre-processed script is also stored in the `munge` folder and processed automatically during loading the project template. After pre-processing, the pre-processed file will be stored in the `cache` folder.

The pre-processing process start from loading all sentiment files in the `data` folder and store into one list. After that, the script will combine all files into one data frame by row. Finally, the pre-processed data frame contains 181 observations with 6 variables.

### 2.4 Modeling
The cluster bar chart below shows the distribution of experience rating. The data shows that most students gave a rating of 3, which is the highest rating, indicating that the course is satisfactory for students. 

```{r, echo=FALSE, fig.width=12, fig.height=3.5, fig.align='center', fig.cap="Distribution of experience rating"}
# Create a complete grid of all possible combinations of run_number and experience_rating
complete_combinations <- expand.grid(
  run_number = unique(preprocessed_sentiment$run_number),
  experience_rating = c(1, 2, 3)
)

# Summarize the data
sentiment_summary <- preprocessed_sentiment |>
  group_by(run_number, experience_rating) |>
  summarize(count = n(), .groups = "drop")

# Merge the complete combinations with the summarized data
sentiment_summary_complete <- complete_combinations |>
  left_join(sentiment_summary, by = c("run_number", "experience_rating")) |>
  mutate(count = ifelse(is.na(count), 0, count)) # Replace NAs with zero counts

# Plot the data
ggplot(sentiment_summary_complete, aes(x = factor(run_number), y = count, fill = factor(experience_rating))) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = count),
            position = position_dodge(width = 0.9), vjust = -0.3, color = "black", size = 4) +
  labs(x = "Run Number",
       y = "Response Count",
       fill = "Experience Rating") +
  theme_minimal() +
  ylim(0, 100) +
  scale_fill_manual(values = c("1" = "#efedf5", "2" = "#bcbddc", "3" = "#756bb1"))
```
For the student feedback, this report analyse by using `syuzhet` library. This library help categories words in each sentence into sentiments including negative and positive. Additionally, the neutral feeling can be then identify if the sentence does not contain any negative or positive sentiments. However, there is no student feedback in the fifth run, thus, this analysis will be performed based on only sixth and seventh runs. The summary of sentiment analysis is illustrated below.

```{r, echo=FALSE, fig.width=10, fig.height=3.5, fig.align='center', fig.cap="Overview of sentiment across each run"}
# Sentiment analysis of 6th run
feedback_run6 <- preprocessed_sentiment[preprocessed_sentiment$run_number == 6, ]

comment_run6 <- iconv(feedback_run6$reason, to = 'utf-8')
sentiment_result_run6 <- get_nrc_sentiment(comment_run6)
sentiment_result_run6$neutral <-
  ifelse(sentiment_result_run6$negative+sentiment_result_run6$positive==0, 1, 0)

sentiment_summary_run6 <- sentiment_result_run6 |>
  select(positive, negative, neutral) |>
  summarise(across(everything(), sum)) |>
  pivot_longer(cols = everything(), names_to = "sentiment", values_to = "count")

# Donut chart plotting
sentiment_summary_run6$fraction <- sentiment_summary_run6$count / sum(sentiment_summary_run6$count)
sentiment_summary_run6$ymax <- cumsum(sentiment_summary_run6$fraction)
sentiment_summary_run6$ymin <- c(0, head(sentiment_summary_run6$ymax, n = -1))
sentiment_summary_run6$labelPosition <- (sentiment_summary_run6$ymax + sentiment_summary_run6$ymin) / 2
sentiment_summary_run6$label <- paste0(sentiment_summary_run6$sentiment, "\n", round(sentiment_summary_run6$fraction * 100, 1), "%")

donut_run6 <- ggplot(sentiment_summary_run6, 
                     aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = sentiment)) +
  geom_rect() +
  geom_label(x = 3.5, aes(y = labelPosition, label = label), size = 4) +
  scale_fill_brewer(palette = "Set2") +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none") +
  labs(title = "Sentiment Analysis - 6th Run")

# Sentiment analysis of 7th run
feedback_run7 <- preprocessed_sentiment[preprocessed_sentiment$run_number == 7, ]

comment_run7 <- iconv(feedback_run7$reason, to = 'utf-8')
sentiment_result_run7 <- get_nrc_sentiment(comment_run7)
sentiment_result_run7$neutral <-
  ifelse(sentiment_result_run7$negative+sentiment_result_run7$positive==0, 1, 0)

sentiment_summary_run7 <- sentiment_result_run7 |>
  select(positive, negative, neutral) |>
  summarise(across(everything(), sum)) |>
  pivot_longer(cols = everything(), names_to = "sentiment", values_to = "count")

# Donut chart plotting
sentiment_summary_run7$fraction <- sentiment_summary_run7$count / sum(sentiment_summary_run7$count)
sentiment_summary_run7$ymax <- cumsum(sentiment_summary_run7$fraction)
sentiment_summary_run7$ymin <- c(0, head(sentiment_summary_run7$ymax, n = -1))
sentiment_summary_run7$labelPosition <- (sentiment_summary_run7$ymax + sentiment_summary_run7$ymin) / 2
sentiment_summary_run7$label <- paste0(sentiment_summary_run7$sentiment, "\n", round(sentiment_summary_run7$fraction * 100, 1), "%")

donut_run7 <- ggplot(sentiment_summary_run7, 
                     aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = sentiment)) +
  geom_rect() +
  geom_label(x = 3.5, aes(y = labelPosition, label = label), size = 4) +
  scale_fill_brewer(palette = "Set2") +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none")  +
  labs(title = "Sentiment Analysis - 7th Run")

grid.arrange(donut_run6, donut_run7, ncol = 2)
```







```{r}
# Assuming `s` is the result of get_nrc_sentiment()
#sentiment_with_polarity <- preprocessed_sentiment %>%
 # mutate(
  #  positive = s$positive,
   # negative = s$negative,
    #sentiment_polarity = positive - negative  # Calculate sentiment polarity
  #)

# View the result
#head(sentiment_with_polarity)

```




